Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-26 paper/paper.tex
Glorious table ;)
Moving stuff around

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.

@@

  \section{Final}

  \begin{table*}
    \centering
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
      \rowcolor{gray!50}
      \textbf{Clusters/capacity} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
        \textbf{$k=2$}& 3~\cite{repartition-disc} & 3~(\S 9.3) \\ 
        \rowcolor{gray!25}
        \textbf{$k=3$}&  $1357\cdot \ell - 245 = \Omega(\ell)$ (\S 9.3)& $O(k \cdot \ell)$~\cite{repartition-disc}\\
        \textbf{$\ell=2$}&  $2k-1$ (\S 9.3)& $O(k^2)$~\cite{repartition-disc}\\
        \rowcolor{gray!25}
        general $k$ and $\ell$& $\Omega(k\cdot \ell)$ (\S 9.3)&$O(k^2 \cdot \ell^2)$~\cite{repartition-disc} \\
      \end{tabular}
                  \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound.
                    }
    \label{tab:overview}
    \vspace{-7mm}
  \end{table*}

  Table with summary of all results. Tight for k=2, asymptotically tight for k=3, and a difference in general lk.

  No bypassing model: reserach.

>>>>

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The overview of results is in Table~\ref{tab:overview}.

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
    \rowcolor{gray!50}
    \textbf{Clusters/capacity} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
      \textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 3\hspace{0.3cm}(\S 9.3) \\ 
      \rowcolor{gray!25}
      \textbf{$k=3$}&  $1357\cdot \ell - 245 = \Omega(\ell)$\hspace{0.3cm}(\S 9.3)& $O(\ell)$\hspace{0.3cm}(\S 9.3)\\
      \textbf{$\ell=2$}&  $2k-1$\hspace{0.3cm}(\S 9.3)&\hspace{0.3cm}$O(k^2)$\hspace{0.3cm}\cite{repartition-disc}\\
      \rowcolor{gray!25}
      general $k$ and $\ell$& $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k^2 \cdot \ell^2)$\hspace{0.3cm}\cite{repartition-disc} \\
    \end{tabular}
                \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound.
                  }
  \label{tab:overview}
  \vspace{-7mm}
\end{table*}

@@
